cardinalR: Generating interesting high-dimensional data structures

### 2025-10-13 paper-cardinalR.Rmd
Add intro paragraph for implementation

```{r, out.width = "100%"}
knitr::include_graphics("figures/cardinalR.pdf")
```

>>>>

The `cardinalR` package is built on a modular framework where individual geometric generators (e.g., Gaussian, cone, sphere) create well-defined shapes. The main function, `gen_multicluster()`, combines these shapes into a single dataset by applying scaling, rotation, and translation through `gen_rotation()`. Each generated shape is assigned a unique cluster label. This design allows flexible construction of complex, high-dimensional structures for evaluating clustering and dimension reduction methods. Figure `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(fig:workflow)', '\\@ref(fig:workflow)'))` illustrates the workflow of `gen_multicluster()`.

```{r workflow, out.width = "100%", fig.pos="H", fig.cap="Workflow of."}
knitr::include_graphics("figures/cardinalR.pdf")
```

### 2025-10-13 paper-cardinalR.tex
Added draft image for the implementation
Add intro paragraph for implementation

>>>>

The \texttt{cardinalR} package is built on a modular framework where individual geometric generators (e.g., Gaussian, cone, sphere) create well-defined shapes. The main function, \texttt{gen\_multicluster()}, combines these shapes into a single dataset by applying scaling, rotation, and translation through \texttt{gen\_rotation()}. Each generated shape is assigned a unique cluster label. This design allows flexible construction of complex, high-dimensional structures for evaluating clustering and dimension reduction methods. Figure \ref{fig:workflow} illustrates the workflow of \texttt{gen\_multicluster()}.

\begin{figure}[H]
\includegraphics[width=1\linewidth]{figures/cardinalR} \caption{Workflow of.}\label{fig:workflow}
\end{figure}
